---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# aor

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/clente/aor/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/clente/aor/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of aor is to help useRs solve the [Advent of
Code](https://adventofcode.com/) in R! It has some helper functions to fetch
puzzles and inputs as quickly as possible.

## Installation

You can install the development version of aor from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("clente/aor")
```

## Authentication

Before using aor, you'll probably want to save your Advent of Code session
cookie as an environment variable; this is necessary for aor to fetch the 2nd
part of puzzles.

In order to find your session cookie, do the following:

1. Navigate to https://adventofcode.com/.
2. Press `F12` to open your browser's developer tools.
3. Select the Network tab.
4. Reload the page.
5. Click on the first request that shows up.
6. Copy the long string after `Cookie: session=`.

Once you have your session cookie, add it to an environment variable called
`AOC_SESSION`. You can do this by running the following command:

```{r, eval=FALSE}
# Add your cookie to .Renviron
readr::write_lines('AOC_SESSION="YOUR_COOKIE"', "~/.Renviron", append = TRUE)
```

If this doesn't work even after restarting R, your can force your session cookie
directly with the following command (just remember to **never upload your cookie
to GitHub**):

```{r, eval=FALSE}
# Set the environment variable directly
Sys.setenv("AOC_SESSION" = "YOUR_COOKIE")
```

## Example

The basic usage of aor revolves around `day_start()` and `day_continue()`. By
default, both functions fetch the **current day's puzzle**, but I'll use
`2022-12-01` as the example here:

```{r}
# Start the puzzle for 2022-12-01 in the aoc2022/ directory
aor::day_start("2022-12-01", "aoc2022/")

# Files created
fs::dir_tree("aoc2022/")
```

Here is what `aoc2022/01_calorie_counting/puzzle.R` looks like (note that I'm
omitting most of the question so that the output is not super long):

```{r, results='asis', echo=FALSE}
txt <- readr::read_lines("aoc2022/01_calorie_counting/puzzle.R")
cat(stringr::str_c(
  "\`\`\`r",
  stringr::str_c(txt[1:8], collapse = "\n"),
  "# ...",
  stringr::str_c(txt[63:71], collapse = "\n"),
  "\`\`\`",
  sep = "\n"
))
```

Once you solve part 1 of the puzzle, you can run the last line of the template
to automatically fetch part 2 into the same file!

```{r}
aor::day_continue("2022-12-01", "aoc2022/01_calorie_counting/puzzle.R")
```

And here is what the file looks like after runing `day_continue()` (again
omitting most of the question):

```{r, results='asis', echo=FALSE}
txt <- readr::read_lines("aoc2022/01_calorie_counting/puzzle.R")
cat(stringr::str_c(
  "\`\`\`r",
  stringr::str_c(txt[1:8], collapse = "\n"),
  "# ...",
  stringr::str_c(txt[63:78], collapse = "\n"),
  "# ...",
  stringr::str_c(txt[88:90], collapse = "\n"),
  "\`\`\`",
  sep = "\n"
))
```

```{r, echo=FALSE}
fs::file_delete("aoc2022/01_calorie_counting/puzzle.R")
fs::file_delete("aoc2022/01_calorie_counting/input.txt")
fs::dir_delete("aoc2022/01_calorie_counting/")
fs::dir_delete("aoc2022/")
```

Good luck! See you on the other side!
